---
output: 
  html_document:
    css: stylesheets/custom_styles.css
    includes: 
      in_header: "header_manual.html" 
params:
  park: MABI
  from: 2006
  to: 2018
  current: 2019
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libs, include = FALSE}
library(NCRNWater)
library(tidyverse)
library(plotly)
library(purrr)
library(htmltools)
library(leaflet)
```

```{r import, cache = TRUE}
#----- Import the data -----
path = "C:/Users/Diana/Documents/NETN/Water/data"
#path = "D:/NETN/R_Dev/Water/NCRNWaterViz/Data/NETN"
netnwd <- importNCRNWater(Dir = path, 
                          Data = "Water Data.csv", 
                          MetaData = "VizMetaData.csv")

```
```{r globvars}
source("../scripts/all_sites_plot.R")

# Long park name
long_name = getParkInfo(netnwd, park = params$park, info = "ParkLongName")

# List of sites
site_list <- getSiteInfo(netnwd, park = params$park, info = "SiteCode")
```

<h1>`r long_name`</h1>
## {.tabset .tabset-fade .tabset-pills}

### Site Comparison
<h2>Comparisons Across Sites (`r params$current`)</h2>
```{r, site_comparison, warning = F, message = F, fig.height=6, out.width='100%'}

site_name <- getSiteInfo(netnwd, parkcode = params$park, sitecode = site_list, info = "SiteName")

char_list <- getCharInfo(netnwd, park = params$park, sitecode = site_list, 
                         category = "physical", info = "CharName") %>% .[duplicated(.)] 
              # only use duplicate chars

plots <- purrr::map(char_list, ~all_sites_plot(params$park, site_list, char = .)) %>%
           set_names(c(char_list)) #name plots to refer to them by char name

# Create grid
plots_final <- subplot(plots$DO_mgL, plots$Temp_C, plots$SpCond_uScm, plots$pH, 
                       titleY = TRUE, titleX = FALSE, nrows=2, margin = 0.05)
plots_final

```
<img src="./images/water_legend_wide_allsites.svg" alt="plot legend" class="legend">

<b>About the figure:</b> The above plots compare monthly measurements across all `r long_name` sites during the `r params$current` field season. Only water quality parameters that are measured at all sites are included.  

```{r, site_tab_setup, cache = T}
# create a function that makes the tab and the plots and then maps to site_list instead of for loop
site_list <- getSiteInfo(netnwd, park = params$park, info = "SiteCode")

char_list <- map(site_list, ~getCharInfo(netnwd, parkcode = params$park, sitecode = ., 
                             category = "physical", info = "CharName")) %>%  
                 set_names(site_list) %>% unlist() %>% as.data.frame()  
                 
char_list$site_code <- substr(row.names(char_list), 1, 14)
colnames(char_list) <- c("char_name", "site_code")
rownames(char_list) <- c()
site_char_list <- char_list[c("site_code", "char_name")]

plot_list <- map2(site_char_list$site_code, site_char_list$char_name, 
                  ~waterbands(netnwd, parkcode = params$park, sitecode = .x, 
                              charname = .y, year_current = params$current,
                              year_historic = params$from)) %>% 
             set_names(site_char_list$site_code) #should name be concatenated site and param?


```

```{r site_tabs, results = 'asis', out.width = '100%', dpi = 300}
# for(i in 1:length(site_list)){
#   site <- site_list[i]
#   subset_plot_list <- plot_list[names(plot_list) == site] #%>%
#                       #.[1:length(.)]
# 
#   fig_height = ifelse(length(subset_plot_list) > 4,
#                       paste0(900),
#                       paste0(600))
#   fig_style = paste0('"height:', fig_height, 'px;"')
# 
#   cat("### ", getSiteInfo(netnwd, parkcode = params$park, sitecode = site,
#                           info = "SiteName"), "\n")
# 
#   print(htmltools::tagList(
#           tags$div(style = paste0(fig_style), #open div, set size with fig_style
#           subplot(subset_plot_list[1:length(subset_plot_list)],
#                          titleY = TRUE, titleX = FALSE, margin = 0.05,
#                          nrows = ifelse(length(subset_plot_list)> 4, 3, 2))
#           ))
#   )
# 
#   cat("\n")
# }

```

```{r fig_height}



```

```{r site_tabs_LDG, results = 'asis', out.width = '100%', dpi = 300}
for(site in site_list){
  subset_plot_list <- plot_list[names(plot_list) == site]

  fig_height = ifelse(length(subset_plot_list) > 4, paste0(900), paste0(600))
  fig_style = paste0('"height:', fig_height, 'px;"')

  cat("### ", getSiteInfo(netnwd, parkcode = params$park, sitecode = site,
                          info = "SiteName"), "\n")

  # cat(paste0("```", "{r ", "fig.height=", fig_height, ", ", "out.width=100%}","\n"))
  # 
  # subplot(subset_plot_list,
  #                        titleY = TRUE, titleX = FALSE, margin = 0.05,
  #                        nrows = ifelse(length(subset_plot_list)> 4, 3, 2))
  # cat("```")

  #  print(htmltools::tagList(
  #         tags$div(style = paste0(fig_style), #open div, set size with fig_style
  #         subplot(subset_plot_list[1:length(subset_plot_list)],
  #                        titleY = TRUE, titleX = FALSE, margin = 0.05,
  #                        nrows = ifelse(length(subset_plot_list)> 4, 3, 2))
  #         ))
  # )
  
  print(withTags(div(
               style = fig_style,
               subplot(subset_plot_list, titleY = TRUE, titleX = FALSE,
                       margin = 0.05, nrows = ifelse(length(subset_plot_list) > 4, 3, 2))
               )))

  cat("\n")
}

```


### Map of Sites 
```{r, leaflet, out.width="100%"}
# source("../scripts/leaflet_tile_urls.R")
# bbox <- read.csv("../boundboxes.csv")  
# 
# long_cent <- mean(c(bbox$LongE[bbox$ParkCode == params$park], bbox$LongW[bbox$ParkCode == params$park]))
# lat_cent <- mean(c(bbox$LatN[bbox$ParkCode == params$park], bbox$LatS[bbox$ParkCode == params$park]))
# 
# water_sites <- data.frame(ParkCode = getSiteInfo(netnwd, parkcode = params$park, info = "ParkCode"),       
#                           SiteCode = getSiteInfo(netnwd, parkcode = params$park, info = "SiteCode"),
#                           SiteName = getSiteInfo(netnwd, parkcode = params$park, info = "SiteName"), 
#                           lat = getSiteInfo(netnwd, parkcode = params$park, info = "lat"),          
#                           long = getSiteInfo(netnwd, parkcode = params$park, info = "long"))
#   
# leaflet() %>%
#     setView(lng = long_cent,
#             lat = lat_cent, 
#             zoom = 14) %>% # Consider making a column in bbox for park-specific zoom value, based on park size
#     setMaxBounds(lng1 = bbox[bbox$ParkCode == params$park,]$LongE, 
#                  lng2 = bbox[bbox$ParkCode == params$park,]$LongW,
#                  lat1 = bbox[bbox$ParkCode == params$park,]$LatN, 
#                  lat2 = bbox[bbox$ParkCode == params$park,]$LatS) %>% 
#     addTiles(group="Map", urlTemplate = NPSbasic, attribution = NPSAttrib) %>%
#     addTiles(group="Imagery", urlTemplate = NPSimagery, attribution=NPSAttrib) %>%
#     addTiles(group="Light", urlTemplate = NPSlight, attribution = NPSAttrib) %>%
#     addTiles(group="Slate", urlTemplate = NPSslate, attribution = NPSAttrib) %>%
#     addLayersControl(map = ., baseGroups = c("Map","Imagery","Light", "Slate"),
#                      options = layersControlOptions(collapsed=T)) %>% 
#   addCircles(data = water_sites,
#              radius = 30,
#              layerId = water_sites$SiteName, 
#              lng = water_sites$long,
#              lat = water_sites$lat,
#              # label = water_sites$SiteName, 
#              # labelOptions = labelOptions(noHide = T, textOnly = TRUE, 
#              #                             direction = 'bottom', textsize = "12px",
#              #                             style = list("color" = "#0365BC",
#              #                                          "font-weight" = "bold")),
#              fillOpacity = 0.9,
#              fillColor = "#0365BC", # fill can be dynamic, based on stream/lake
#              color = "DimGrey", # outline color
#              popup = water_sites$SiteName, # create more content for this popup message
#              weight = 1.5) #outline thickness

```

